---
title: "Sunbird"
author: "Connor J Barr"
format: html
editor: visual
---

### Required Packages

```{r}
library(dplyr)
library(ggplot2)
library(tidyverse)
```

### Read in the CSV file

```{r}

#Read the data in
Sunbirds.rep <- read_csv("Data.csv")

#Print a summary of the data
Sunbirds.rep
```

Now the datasheet is in R.

### Tidy the data

Create a new column (Active_birds) which sums all the activities recorded along one transect for a specific time of day. Filter the data to just 4 columns.

```{r}

Sunbirds.mutate <- Sunbirds.rep %>% 
              mutate("Active_birds" = feeding + flying + resting + preening + calling + chasing) %>%
   select("species", "sex", "time_of_day", "Active_birds")

Sunbirds.mutate
```

Combine the Sex and Species

```{r}

Sunbirds.tidy <- Sunbirds.mutate %>%
                    unite("Sp.sex", species:sex, sep = "_")
  
Sunbirds.tidy
```

### Create a preliminary plot

Plot a box plot showing the activity of each species and sex during the three different times of day.

```{r}

ggplot.Sunbirds <- Sunbirds.tidy %>% 
  ggplot(aes(time_of_day, Active_birds, colour = Sp.sex)) +
  geom_jitter(height = 0.01, alpha = 0.7) +
  facet_wrap(~Sp.sex , nrow=2) + 
  labs(x = "Time of day",
       y= "Number of active birds",
       title="Sunbirds active at different time periods by species and sex") +
  theme_bw() + geom_boxplot() +
  stat_summary(fun=mean, geom="point", shape=23, size=4)


ggplot.Sunbirds
```
